---
title: "charades-plotting"
format: html
editor: visual
---

## How to Play

Put a plot up on a projector from the penguins data set and have 1 person on the team face away from the projector and be the designated “coder”

The teammates, who could see the projector, had to tell them what to plot (variables, type of plot, colors etc) without using any words.

Everyone posts their plot in slack and then the winning team (team with the closest plot) gets a prize.

## Plots to show 

```{r}

library(tidyverse)
library(palmerpenguins)

```


### Plot 1 

```{r}
 
penguins |>
  ggplot(aes(
    x = flipper_length_mm, y = bill_length_mm , color = species
  )) + 
    geom_point() + 
    geom_smooth(se = F) + 
  labs(
    title = "Bill and Flipper Length by Species"
  )


```


### Plot 2

```{r}

penguins |>
  ggplot(
    aes(x = species)) + 
  geom_bar() + 
  facet_wrap(~island) + 
  labs(title = "Species facet by Island")

```


### Plot 3 

```{r}
penguins |>
  ggplot(
    aes(x = bill_depth_mm, y = sex)
  ) + 
  geom_boxplot(notch = TRUE) + 
  labs(title = "Boxplot of bill depth by sex")


```


### Plot 4 

```{r}
penguins |>
  ggplot(
    aes(x = body_mass_g)) + 
      geom_density(color = "blue" , fill = "white") + 
  labs(title = "Density plot of body mass")


```




### Plot 5 

```{r}
penguins |>
  ggplot(
    aes(x = island, y = flipper_length_mm)
  ) + 
  geom_col(aes(color = sex, fill = sex), position = position_stack()) +
  labs(title = "Flipper length by island stacked and colored by sex")
  

```

